\input{template_settings/ch_preamble}
\begin{document}
\input{template_settings/common/renames}
\begin{abstr}
Name SecondName Surname of First Author, scientific degree, title of the position, organization, a address, %
\mailtoMLABSEDauthor{email@spbstu.ru}{Dear Author}{email@spbstu.ru}.
\par
Name SecondName Surname of Second Author, scientific degree,  title of the position, organization, a address, %
\mailtoMLABSEDauthor{email@spbstu.ru}{Dear Author}{email@spbstu.ru}.
\par
{\normalfont \abstractnameENG.} The text of the abstract in english (at least 70 and at most 150 words).
\par
{\normalfont \keywordsENG.} Three-six comma separated keywords.
\par
{\normalfont \acknowledgementsENG.} Acknowledgements, information about supporting grants and funds. Can be omitted.
\delnewpagebeforech
\chapter*{\normalsize \chapterRuTitle}
Имя Отчество Фамилия первого автора, степень, должность, организация, адрес, \mailtoMLABSEDauthor{email@spbstu.ru}{Dear Author}{email@spbstu.ru}. %{true email}{email body}{represented email}
\par
Имя Отчество Фамилия второго автора, степень, должность, организация, адрес, \mailtoMLABSEDauthor{email@spbstu.ru}{Dear Author}{email@spbstu.ru}. %{true email}{email body}{represented email}
\par
{\normalfont \abstractname.} Текст аннотации на русском (минимум 70 и максимум 150 слов).
\par
{\normalfont \keywords.} 6-7 ключевых слов через запятую.
\par
{\normalfont \acknowledgements.} Благодарности, информация о поддерживающих грантах и фондах. При необходимости. 
\end{abstr}
\end{document}
